BACI of biomass change for VOCC source cells for all years

### 2019-09-30 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
correct typo in root value selection for temperature

  if (biomass_threshold == "75") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75 }
  if (biomass_threshold == "50") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)

@@

  if (biomass_threshold == "75") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75 }
  if (biomass_threshold == "50") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)
  upper_thresholds <- round(.upper[1], digits = 2)

>>>>

 # if more than one model option in dataframe will pick the one with highest peak density
  if (biomass_threshold == "75") {
  .upper <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75 }
  if (biomass_threshold == "50") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)

@@

  if (biomass_threshold == "75") {
  .upper <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75 }
  if (biomass_threshold == "50") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)
  upper_thresholds <- round(.upper[1], digits = 2)
